\documentclass[14pt]{article}
\usepackage{graphicx}
\begin{document}


\title{A REPORT ABOUT THE USE OF MOBILE PHONES IN LECTURES.}

\author{BY ARYATWIJUKA JUDITH.REG.NO. 15/U/3718/PS. ST.NO.215004216}

\date{\today}

\maketitle

\tableofcontents

\section{Abstract}

The aim of this report is to investigate students’ attitudes to personal phone use in lectures. A survey on attitudes towards the use of mobile phones in lectures was conducted and the results indicate that the majority of students find mobile phone use in lectures a major issue. The report concludes that personal mobile phones are disruptive and should be turned off in lectures

\section{Introduction}

There has been a massive increase in the use of personal mobile phones over the last two years and there is every indication that this will continue especially in university students.

\section{Methods}

This research was conducted by interviewing students about the attitudes to the use of mobile phones in lectures.

\section{Results}

There was a high response to the interviews and from the results it can be clearly seen that mobile phones are considered to be disruptive and should be turned off in lectures.
Use of phone in lectures	Agree 	Disagree 
Not a problem	              7	                       15
An issue	                   20                                 2            	
Disruptive 	                       22	                          0                   
Phones should be permissible	10	12
Phones should be turned off	21	1
Allowed in some circumstances	11	11


\subsection{Discussion about results}

It can be seen from the results that personal mobile phone use is considered to be a problem. However it is good that in some situation it should be permissible. Most students considered phones to be highly disruptive and there was a strong support for phones being turned off in lectures.

\section{Conclusion}

The use of mobile phones in lectures is clearly disruptive and they should be switched off. Most students felt it is not necessary to receive personal phone calls in lectures except under certain circumstances but permission should be sought first from the lecturer.

\section{Recommendations}

It is recommended that the university develops a policy regarding the use of mobile phones in lectures. The policy should recommend:
•	Mobile phones are banned in lectures.
•	Mobile phones may be used in exceptional circumstances but only with the permission of the appropriate lecturer.
Finally, the policy needs to apply to all students in the university.
 









\end{document}